MaBoSS for HPC environments: Implementations of the continuous time Boolean model simulator for large CPU clusters and GPU accelerators

### 2024-03-03 Article.tex
a few edits, a few todos
plot some plotty things

% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
\author[1,\authfn{1}]{Adam Šmelko}
\author[2]{Miroslav Kratochvíl}
\author[3,4,5]{Emmanuel Barillot}
\author[3,4,5]{Laurence Calzone}
\author[3,4,5,\authfn{1}]{Vincent Noël}

@@

\begin{algorithm}
\caption{A single iteration of the MaBoSS simulation of a trajectory, given the state $S$ and time $t$.}
\label{alg:iter}
\begin{algorithmic}[1]
\Procedure{TrajectorySimulationStep}{S, t}
\State $\rho_1 \gets \mathcal{B}_1(S), \dots, \rho_n \gets \mathcal{B}_n(S)$ \Comment compute transition rates
\State $r \gets \text{random}([0, \sum_{i=1}^n \rho_i))$
\State $i \gets \min_i \sum_{j=1}^{i-1} \rho_j \leq r < \sum_{j=1}^{i} \rho_j$ \Comment select a node for flipping
\State $S'\gets S\ \text{with the $i$-th bit flipped}$
\State $u \gets \text{random}([0, 1])$
\State $\delta t \gets -\frac{\ln u}{\sum_{i=1}^n \rho_i}$
\State \textbf{return} $(S', t + \delta t)$
\EndProcedure
\end{algorithmic}
%TODO this should be in a float/figure (\begin{algorithm} etc)
\end{algorithm}

@@

\begin{figure}%[tbhp]
\centering
\includegraphics[width=.8\linewidth]{Figures/sizek_mpi.pdf}
\caption{Scalability results of MPI implementation on Sizek model with 20 cores per MPI node.}
\label{fig:sizek_results}
\end{figure}

@@

\begin{figure}%[tbhp]
\centering
\includegraphics[width=.8\linewidth]{Figures/synth_mpi_speedup.pdf}
\caption{Speedup scaling of MPI implementation on a synthetic model with 1000 nodes and 32 cores per MPI node.}
\label{fig:synthetic_results}
\end{figure}

@@

\section{Acknowledgements}
We thank Gautier Stoll for his guidance and fruitful discussion.

>>>>

% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
\author[1,\authfn{1}]{Adam Šmelko}
\author[2]{Miroslav Kratochvíl}
\author[3,4,5]{Emmanuel Barillot}
% \author[3,4,5]{Laurence Calzone}
\author[3,4,5,\authfn{1}]{Vincent Noël}

@@

\begin{algorithm}
\caption{A single iteration of the MaBoSS simulation of a trajectory, given the state $S$ and time $t$.}
\label{alg:iter}
\begin{algorithmic}[1]
\Procedure{TrajectorySimulationStep}{S, t}
\State $\rho_1 \gets \mathcal{B}_1(S), \dots, \rho_n \gets \mathcal{B}_n(S)$ \Comment compute transition rates
\State $r \gets \text{random}([0, \sum_{i=1}^n \rho_i))$
\State $i \gets \min_i \sum_{j=1}^{i-1} \rho_j \leq r < \sum_{j=1}^{i} \rho_j$ \Comment select a node for flipping
\State $S'\gets S\ \text{with the $i$-th bit flipped}$
\State $u \gets \text{random}([0, 1])$
\State $\delta t \gets -\frac{\ln u}{\sum_{i=1}^n \rho_i}$
\State \textbf{return} $(S', t + \delta t)$
\EndProcedure
\end{algorithmic}
\end{algorithm}

@@

\begin{figure}%[tbhp]
\centering
\includegraphics[width=3.25in]{Figures/sizek_mpi.pdf}
\caption{Scalability results of MPI implementation on Sizek model with 20 cores per MPI node.}
\label{fig:sizek_results}
\end{figure}

@@

\begin{figure}%[tbhp]
\centering
\includegraphics[width=3.25in]{Figures/synth_mpi_speedup.pdf}
\caption{Speedup scaling of MPI implementation on a synthetic model with 1000 nodes and 32 cores per MPI node.}
\label{fig:synthetic_results}
\end{figure}

@@

\section{Acknowledgements}
We thank Laurence Calzone and Gautier Stoll for their guidance and fruitful discussions.
